---
title             : "**Supplementary materials**"
shorttitle        : "Character strengths, well-being, and ill-being"
author: 
  - name          : "BLINDED"
# abstract: |
# keywords          : "character strengths; meta-analysis; well-being; mental health; review"
wordcount         : "0000"
bibliography      : "paper.bib"
figsintext        : yes
floatsintext      : no
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa6"
classoption       : "man"
output: 
    papaja::apa6_docx: default
    papaja::apa6_pdf:
        latex_engine: xelatex
        in_header: header.tex
        toc: true
        toc_depth: 2
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1,footnotesize}}
  - \usepackage{float}
  - \usepackage{lscape}
  - \usepackage{rotating}
  - \usepackage{orcidlink}
  - \usepackage{xcolor}
  - \usepackage{soul}
  - \sethlcolor{red}
  - \newcommand{\rev}{\color{red}}
  - \newcommand{\erev}{\color{black}}
  - \usepackage[margin=1in, left=1in, right=1in]{geometry}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    fig.align = "center",
    comment = "#>",
    size = "footnotesize",
    dev = c("pdf", "tiff")
)
options(tinytex.verbose = TRUE)
options(knitr.table.format = "latex")
```

```{r packages, include = FALSE}
# Writing packages
library(papaja)
library(kableExtra)
library(here)
library(knitr)
library(flextable)
# Analysis packages
library(ggplot2)
library(metafor)
library(readxl)
library(dplyr)
library(pacman)

# utils functions for the paper
output_format <- knitr::opts_knit$get("rmarkdown.pandoc.to")
source(here("paper", "utils-paper.R"), local = knitr::knit_global())
# 
folder_path <- "R"  # Adjust this if the folder is located elsewhere
r_files <- list.files(folder_path, full.names = TRUE, pattern = "\\.R$")
for (r_file in r_files) {
  source(r_file)  # This will run the R code in the specified script file
}

load("results/strengths.R")
resList <- readRDS("results/resList.RDS")
effList <- readRDS("results/effList.RDS")
d = read_excel("results/d_final.xlsx")
strengths <- colnames(d[, which(colnames(d) == "Appreciation_of_beauty"):
                          which(colnames(d) == "Self-control")])
strengths24 <- colnames(d[, which(colnames(d) == "Appreciation_of_beauty"):
                            which(colnames(d) == "Zest")])
d[d$Valence == "neg", strengths] <- d[d$Valence == "neg", strengths] * -1

# Create dataset without virtues
dtot <- d[, !names(d) %in% c("CVQ_cautiousness", "CVQ_interpersonal", 
                             "CVQ_vitality", "Caring", 
                             "Inquisitiveness", "Self-control")]
max(rowSums(apply(dtot[,strengths24], 2, is.na)))
dtot <- dtot[rowSums(apply(dtot[,strengths24],2,is.na))<24, ]
max(rowSums(apply(dtot[,strengths24], 2, is.na)))

# Create dataset with non-duplicated samples for descriptive stats
uniqueD <- dtot[!duplicated(dtot$sample), ]
```

\newpage
# Descriptive statistics

```{r}
# Create a dataframe with one line per strength (+3*2 virtues) and one column per information
summStat <- data.frame(strength = strengths,
                       N_studies = rep(NA, 30),
                       N_samples = rep(NA, 30),
                       k = rep(NA,30),
                       N = rep(NA,30),
                       Sample_Size = rep(NA,30),
                       CS_short = rep(NA,30),
                       CS_long = rep(NA,30),
                       CS_other = rep(NA,30),
                       # Specific CS measure,
                       Wellbeing = rep(NA,30),
                       MentalHealt = rep(NA,30),
                       # SpecificOutcome,
                       # Countries,
                       Clinical = rep(NA, 30),
                       Youth = rep(NA,30),
                       Adult = rep(NA,30),
                       Old = rep(NA,30)
                       )

# Calculate each info for each skill by subsetting the data
for (i in 1:length(strengths)) {
  dsum <- d[is.na(d[,strengths[i]]) == F, ]
  summStat[i, 2:ncol(summStat)] <- c(length(unique(dsum$ID)),
                                     length(unique(dsum$sample)),
                                     nrow(dsum),
                                     #sum(dsum$N[dsum$sample %in% unique(dsum$sample)], na.rm = TRUE),
                                     sum(dsum$N[!duplicated(dsum$ID)], na.rm = TRUE),
                                     paste0("[", min(dsum$N,na.rm=TRUE), "; ", max(dsum$N,na.rm=TRUE),"]"),
                                     sum(dsum$CS_measure=="short",na.rm=TRUE),
                                     sum(dsum$CS_measure=="long",na.rm=TRUE),
                                     sum(dsum$CS_measure=="other",na.rm=TRUE),
                                     sum(dsum$Outcome=="wb",na.rm=TRUE),
                                     sum(dsum$Outcome=="mh",na.rm=TRUE),
                                     sum(dsum$Population=="clinical",na.rm=TRUE),
                                     sum(dsum$Age_classification=="young",na.rm=TRUE),
                                     sum(dsum$Age_classification=="adult",na.rm=TRUE),
                                     sum(dsum$Age_classification=="old",na.rm=TRUE)
                                     )
}

# Stats for the total sample, without virtues (these are excluded because we won't meta-analyze them)
# Calculate each info for the total sample
totStat <- c("FullSample",
             length(unique(dtot$ID)),
             length(unique(dtot$sample)),
             sum(is.na(dtot[,strengths24])==FALSE),
             sum(dtot$N[!duplicated(dtot$ID)], na.rm = TRUE),
#             sum(dtot$N[dtot$sample %in% unique(dtot$sample)], na.rm = TRUE),
             paste0("[", min(dtot$N,na.rm=TRUE), "; ", max(dtot$N,na.rm=TRUE),"]"),
             sum(as.numeric(summStat$CS_short[1:length(strengths24)])),
             sum(as.numeric(summStat$CS_long[1:length(strengths24)])),
             sum(as.numeric(summStat$CS_other[1:length(strengths24)])),
             sum(as.numeric(summStat$Wellbeing[1:length(strengths24)])),
             sum(as.numeric(summStat$MentalHealt[1:length(strengths24)])),
             sum(as.numeric(summStat$Clinical[1:length(strengths24)])),
             sum(as.numeric(summStat$Youth[1:length(strengths24)])),
             sum(as.numeric(summStat$Adult[1:length(strengths24)])),
             sum(as.numeric(summStat$Old[1:length(strengths24)]))
)

TableStat <- data.frame(rbind(summStat, totStat))
colnames(TableStat)<-gsub("_", " ", colnames(TableStat))
knitrMeta(TableStat,output_format
          ,
          capt="Descriptive statistics",
          foot="FullSample stats exclude papers with only virtues"
          )
```

\newpage
# Detailed results on mental health vs well-being moderator analysis
```{r}
modRes = effList[["mainMod"]]
Table3 <- data.frame(
  Strength = modRes$strength,
  r_MH = paste0(format(modRes$r0,nsmall = 3),
                       " [",format(modRes$rcil0,nsmall = 3),"; ",
                       format(modRes$rciu0,nsmall = 3),"]"),
  N_MH = modRes$N0,
  k_MH = modRes$k0,
  r_WB   = paste0(format(modRes$r1,nsmall = 3),
                       " [",format(modRes$rcil1,nsmall = 3),"; ",
                       format(modRes$rciu1,nsmall = 3),"]"),
  N_WB = modRes$N1,
  k_WB = modRes$k1,
  delta_r = paste0(format(modRes$deltaR, nsmall = 3),ifelse(modRes$p < .01, "*", "")),
  delta_CI = paste0("[",format(modRes$cil,nsmall = 3),"; ",
                   format(modRes$ciu,nsmall = 3),"]"),
  se = format(modRes$se,nsmall = 3), 
  z = format(modRes$z,nsmall = 3),
  tau2 = format(modRes$tau2,nsmall = 3),
  Q =paste0(format(modRes$q), ifelse(modRes$qp < .01, "*", "")), #"(",modRes$qdf,")",
  QM =paste0(format(modRes$qM), ifelse(modRes$qMp < .01, "*", "")) #"(",modRes$qMdf,")",
)
colnames(Table3)<-gsub("_", " ", colnames(Table3))
knitrMeta(Table3,output_format,
          capt="Moderator analysis testing for differences between mental health (MH) and well-being (WB) outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```

\newpage
# Detailed results on clinical vs non-clinical population (WB)

```{r}
wbmodPopRes <- effList[["wbPop"]]
Table4 <- data.frame(Strength = wbmodPopRes$strength, 
                     r_clinical = paste0(round(wbmodPopRes$r0,3),
                                       " [",round(wbmodPopRes$rcil0,3),"; ",
                                       round(wbmodPopRes$rciu0,3),"]"),
                     N = wbmodPopRes$N0,
                     k = wbmodPopRes$k0,
                     r_not_clinical = paste0(round(wbmodPopRes$r1,3),
                                            " [",round(wbmodPopRes$rcil1,3),"; ",
                                            round(wbmodPopRes$rciu1,3),"]"),
                     N_ = wbmodPopRes$N1,
                     k_ = wbmodPopRes$k1,
                     delta_r = paste0(format(wbmodPopRes$deltaR, nsmall = 3),ifelse(modRes$p < .01, "*", "")),
                     delta_CI = paste0("[",format(wbmodPopRes$cil,nsmall = 3),"; ",
                                      format(wbmodPopRes$ciu,nsmall = 3),"]"),
                     se = format(wbmodPopRes$se,nsmall = 3), 
                     z = format(wbmodPopRes$z,nsmall = 3),
                     #p = format(wbmodPopRes$p,4),
                     tau2 = wbmodPopRes$tau2,
                     Q =paste0(format(wbmodPopRes$q), ifelse(wbmodPopRes$qp < .01, "*", "")),#"(",wbmodPopRes$qdf,")",
                     QM =paste0(format(wbmodPopRes$qM), ifelse(wbmodPopRes$qMp < .01, "*", "")) #"(",wbmodPopRes$qMdf,")",
                     
)
colnames(Table4)<-gsub("_", " ", colnames(Table4))
knitrMeta(Table4,output_format,
          capt="Moderator analysis testing for differences between clinical and non-clinical population on WB outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```

\newpage
# Detailed results on short vs long VIA formats (WB)
```{r}
wbmodViaRes <- effList[["wbVia"]]
Table5 <- data.frame(Strength=wbmodViaRes$strength,
                     r_long = paste0(round(wbmodViaRes$r0,3),
                                   " [",round(wbmodViaRes$rcil0,3),"; ",
                                   round(wbmodViaRes$rciu0,3),"]"),
                     N = wbmodViaRes$N0, 
                     k = wbmodViaRes$k0,
                     r_short   = paste0(round(wbmodViaRes$r1,3),
                                      " [",round(wbmodViaRes$rcil1,3),"; ",
                                      round(wbmodViaRes$rciu1,3),"]"),
                     N_ = wbmodViaRes$N1, 
                     k_ = wbmodViaRes$k1,
                     delta_r = paste0(format(wbmodViaRes$deltaR, nsmall = 3),ifelse(wbmodViaRes$p < .01, "*", "")),
                     delta_CI = paste0("[",format(wbmodViaRes$cil,nsmall = 3),"; ",
                                      format(wbmodViaRes$ciu,nsmall = 3),"]"),
                     se = format(wbmodViaRes$se,nsmall = 3), 
                     z = format(wbmodViaRes$z,nsmall = 3),
                     #p = format(wbmodViaRes$p,4),
                     tau2 = wbmodViaRes$tau2,
                     Q =paste0(format(wbmodViaRes$q), ifelse(wbmodViaRes$qp < .01, "*", "")),#"(",wbmodViaRes$qdf,")",
                     QM =paste0(format(wbmodViaRes$qM),ifelse(wbmodViaRes$qMp < .01, "*", "")) #, "(",wbmodViaRes$qMdf,")"
)
colnames(Table5)<-gsub("_", " ", colnames(Table5))
knitrMeta(Table5,output_format,
          capt="Moderator analysis testing for differences between short and long VIA formats on WB outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```

\newpage
# Detailed results on specific well-being outcomes
```{r}
wbmodwbRes <- effList[["wbwb"]]
Table6 <- data.frame(Strength = wbmodwbRes$strength,
                     Domain_satisfaction = paste0(format(wbmodwbRes$r1,nsmall=2),
                                        " [",format(wbmodwbRes$rcil1,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu1,nsmall=2),"]"),
                     Happyness = paste0(format(wbmodwbRes$r2,nsmall=2),
                                        " [",format(wbmodwbRes$rcil2,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu2,nsmall=2),"]"),
                     Life_satisfaction = paste0(format(wbmodwbRes$r3,nsmall=2),
                                        " [",format(wbmodwbRes$rcil3,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu3,nsmall=2),"]"),
                     Negative_affect = paste0(format(wbmodwbRes$r4,nsmall=2),
                                        " [",format(wbmodwbRes$rcil4,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu4,nsmall=2),"]"),
                     Positive_affect = paste0(format(wbmodwbRes$r5,nsmall=2),
                                        " [",format(wbmodwbRes$rcil5,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu5,nsmall=2),"]"),
                     Psychological_wellbeing = paste0(format(wbmodwbRes$r6,nsmall=2),
                                        " [",format(wbmodwbRes$rcil6,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu6,nsmall=2),"]"),
                     Subjective_wellbeing = paste0(format(wbmodwbRes$r7,nsmall=2),
                                        " [",format(wbmodwbRes$rcil7,nsmall=2),"; ",
                                        format(wbmodwbRes$rciu7,nsmall=2),"]"),
                     Overall_effect= paste0(format(modRes$r1,nsmall=2),
                                        " [",format(modRes$rcil1,nsmall=2),"; ",
                                        format(modRes$rciu1,nsmall=2),"]"),
                     tau2 = wbmodwbRes$tau2,
                     Q =paste0(format(modRes$q), "(",modRes$qdf,")",ifelse(modRes$qp < .01, "*", "")),
                     QM =paste0(format(modRes$qM), "(",modRes$qMdf,")",ifelse(modRes$qMp < .01, "*", ""))
)
colnames(Table6)<-gsub("_", " ", colnames(Table6))
knitrMeta(Table6,output_format,
          capt="Moderator analysis testing for differences between specific WB outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```

\newpage
# Detailed results on clinical vs non-clinical populations (MH)
```{r}
mhmodPopRes = effList[["mhPop"]]
Table7 <- data.frame(Strength = mhmodPopRes$strength,
                     r_MH = paste0(round(mhmodPopRes$r0,2),
                                           " [",round(mhmodPopRes$rcil0,2),"; ",
                                           round(mhmodPopRes$rciu0,2),"]"),
                      N_MH = mhmodPopRes$N0, 
                      k_MH = mhmodPopRes$k0,
                      r_WB = paste0(round(mhmodPopRes$r1,2),
                                           " [",round(mhmodPopRes$rcil1,2),"; ",
                                           round(mhmodPopRes$rciu1,2),"]"),
                      N_WB = mhmodPopRes$N1, 
                      k_WB = mhmodPopRes$k1, 
                      delta_r = paste0(format(mhmodPopRes$deltaR, nsmall = 2),ifelse(mhmodPopRes$p < .01, "*", "")),
                      delta_CI = paste0("[",format(mhmodPopRes$cil,nsmall = 2),"; ",
                                       format(mhmodPopRes$ciu,nsmall = 2),"]"),
                      se = format(mhmodPopRes$se,nsmall = 2), 
                      z = format(mhmodPopRes$z,nsmall = 2),
                      # p = format(mhmodPopRes$p,4),
                      tau2 = mhmodPopRes$tau2,
                      Q =paste0(format(mhmodPopRes$q), ifelse(mhmodPopRes$qp < .01, "*", "")),#"(",mhmodPopRes$qdf,")",
                      QM =paste0(format(mhmodPopRes$qM), ifelse(mhmodPopRes$qMp < .01, "*", "")) #"(",mhmodPopRes$qMdf,")",
                      
)
colnames(Table7)<-gsub("_", " ", colnames(Table7))
knitrMeta(Table7,output_format,
          capt="Moderator analysis testing for differences between clinical and non-clinical populations on MH outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```

\newpage
# Detailed results on short vs long VIA formats (MH)
```{r}
mhmodViaRes <- effList[["mhVia"]]
Table8 <- data.frame(Strength = mhmodViaRes$strength,
                     r_long = paste0(round(mhmodViaRes$r0,2),
                                    " [",round(mhmodViaRes$rcil0,2),"; ",
                                    round(mhmodViaRes$rciu0,2),"]"),
                      N = mhmodViaRes$N0, 
                      k = mhmodViaRes$k0, 
                      r_short   = paste0(round(mhmodViaRes$r1,2),
                                       " [",round(mhmodViaRes$rcil1,2),"; ",
                                       round(mhmodViaRes$rciu1,2),"]"),
                      N_ = mhmodViaRes$N1, 
                      k_ = mhmodViaRes$k1,
                      delta_r = paste0(format(mhmodViaRes$deltaR, nsmall = 2),ifelse(mhmodViaRes$qp < .01, "*", "")),
                      delta_CI = paste0("[",format(mhmodViaRes$cil,nsmall = 2),"; ",
                                       format(mhmodViaRes$ciu,nsmall = 2),"]"),
                      se = format(mhmodViaRes$se,nsmall = 2), 
                      z = format(mhmodViaRes$z,nsmall = 2),
                      #p = format(mhmodViaRes$p,4),
                      tau2 =mhmodViaRes$tau2,
                      Q =paste0(format(mhmodViaRes$q),ifelse(mhmodViaRes$qp < .01, "*", "")),#, "(",mhmodViaRes$qdf,")"
                      QM =paste0(format(mhmodViaRes$qM),ifelse(mhmodViaRes$qMp < .01, "*", ""))#, "(",mhmodViaRes$qMdf,")"
)
colnames(Table8)<-gsub("_", " ", colnames(Table8))
knitrMeta(Table8,output_format,
          capt="Moderator analysis testing for differences between short and long VIA formats on MH outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```

\newpage
# Detailed results on specific mental health outcome
```{r}
mhmodmhRes <- effList[["mhmh"]]
Table9 <- data.frame(Strength = mhmodmhRes$strength,
                     Anxiety = paste0(round(mhmodmhRes$r1,2),
                                                  " [",round(mhmodmhRes$rcil1,2),"; ",
                                                  round(mhmodmhRes$rciu1,2),"]"),
                     Depression = paste0(round(mhmodmhRes$r2,2),
                                         " [",round(mhmodmhRes$rcil2,2),"; ",
                                         round(mhmodmhRes$rciu2,2),"]"),
                     General_mental_health = paste0(round(mhmodmhRes$r3,2),
                                                  " [",round(mhmodmhRes$rcil3,2),"; ",
                                                  round(mhmodmhRes$rciu3,2),"]"),
                     Stress = paste0(round(mhmodmhRes$r4,2),
                                     " [",round(mhmodmhRes$rcil4,2),"; ",
                                     round(mhmodmhRes$rciu4,2),"]"),
                     Overall_effect = paste0(round(modRes$r0,2),
                                             " [",round(modRes$rcil0,2),"; ",
                                             round(modRes$rciu0,2),"]"),
                     tau2 = mhmodmhRes$tau2,
                      Q =paste0(format(modRes$q), ifelse(modRes$qp < .01, "*", "")),#"(",modRes$qdf,")",
                      QM =paste0(format(modRes$qM), ifelse(modRes$qMp < .01, "*", ""))#"(",modRes$qMdf,")",
)
colnames(Table9)<-gsub("_", " ", colnames(Table9))
knitrMeta(Table9,output_format,
          capt="Moderator analysis testing for differences between specific MH outcomes",
          foot="QM indicates the Q test for the moderator analysis")
```


\newpage
# Table results overall

```{r}
metaRes <- effList[["overall"]]

Table2 <- data.frame(
  Strength = metaRes$strength,
  N = metaRes$N,
  k = metaRes$k,
  r = paste0(format(round(metaRes$r, 3),nsmall=3),ifelse(metaRes$p < .01, "*", "")),
  CI = paste0("[",format(round(metaRes$rcil,3),nsmall=3),"; ",
              format(round(metaRes$rciu,3),nsmall=3),"]"),
  se = format(round(metaRes$se,3),nsmall=3), 
#  p = format(round(metaRes$p,4),3),
  tau2 = format(round(metaRes$tau2,3),nsmall=3),
  Q =paste0(round(metaRes$q), ifelse(metaRes$qp < .01, "*", ""))#"(",metaRes$qdf,")",
  )

knitrMeta(Table2,output_format,scaled=FALSE,
          capt="Meta-analytical associations between character strengths and mental health and well-being",
          foot="See the shiny app for additional info"
          )

```
